\documentclass{resume} % Use the custom resume.cls style

\usepackage{xcolor}
\usepackage{hyperref}
\definecolor{linkcolor}{HTML}{000080} % ???? ??????
\definecolor{urlcolor}{HTML}{000080} % ???? ???????????
\hypersetup{pdfstartview=FitH,  linkcolor=linkcolor,urlcolor=urlcolor, colorlinks=true}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Daniil Kochergin}

\begin{document}

\begin{rSection}{Education}

{{\bf Student of ITMO University, Saint Petersburg} \hfill {\em 2018 -- Present} 
\\ Third-year student, Computer Science and Applied Math department.}
\end{rSection}
\begin{rSection}{Projects and achievements} 
{\bf \href{http://sesc.nsu.ru/vsesib/inf.html}{Winner of country-level school olympiad}} \hfill {\em 2017} \\
Winner of the first degree in competitive programming olympiad. \vskip 0.4\\
{{\bf \href{https://olymp.innopolis.ru/shop/}{Summer informatics school}} \hfill {\em 2017} \\
Studied algorithms and data structures. \vskip 0.4\\}
{{\bf \href{https://github.com/ZloyTapok987/Project}{Android application}} \hfill {\em 2018} \\
With my team developed networking application on Java. \vskip 0.4\\}
{{\bf \href{https://github.com/DaniilKochergin/CppCourse/tree/master/helloasm}{Big integer in Assembler}} \hfill {\em 2018} \\
Implemented addition, subtraction and multiplication. \vskip 0.4\\}
{{\bf \href{https://github.com/DaniilKochergin/huffman}{Console utility for Huffman encoder/decoder in C++}} \hfill {\em 2019} \\
Implemented an utility whose interface allows compress/decompress files larger than RAM.\vskip 0.4 \\}
{{\bf Async client in C++} \hfill {\em 2019}  \\
Thread safe client which manage requests. Application has metrics and statement coverage.}
\end{rSection}

\begin{rSection}{Programming languages and skills}
{\bf {\large Programming languages} \hspace{138pt} {\large Skills}}
\begin{itemize}
    \item {{\bf C++}  \hspace{240pt} \labelitemi { {\bf Alghoritms \& data structures}}  \\
    QTcreator, Sanitizers, C++17, boost library} 
    \item { {\bf Java } \hspace{240pt} \labelitemi{ {\bf Multithreading}} \\
    Streams, Android Studio, standart library}
    \item {{\bf Python }} \hspace{224pt} \labelitemi { {\bf Object Oriented Development}} 
    \\ Basic syntax
    \item {{\bf Clojure, Haskell }} \hspace{175pt} \labelitemi { {\bf Machine learning}}
    \\ Use in educational projects in the university
\end{itemize}


\end{rSection}


\begin{rSection}{Work Experience}

\begin{rSubsection}{Yandex, Moscow}{ {\em 2019}}{C++ Backend developer intern}{}
\item Develop distributed build system. Learned and implemented aspects such as  {\bf database}, {\bf multithreading}, {\bf bash scripts} and {\bf KVM}.
\end{rSubsection}

\begin{rSubsection}
{Huawei, Saint Petersburg} {\em 2020 -- Present} {Compiler team intern} {}
\end{rSubsection}

\end{rSection}


\begin{rSection} {Contacts}
 \textbf{Phone:} +79967855387 \hspace{0.8cm} \textbf{Email:} kochergin-2000@mail.ru \hspace{0.8cm} \textbf{Telegram:} \href{http://t.me/DanilKochergin}{DanilKochergin} 
 \item \textbf{Github:} \href{http://github.com/DaniilKochergin}{DaniilKochergin}
\end{rSection}
\end{document}
